Capital Budget Funding in Toronto

### 2024-09-27 paper/paper.qmd
updated paper.pdf

These datasets were merged in order to link capital funding allocations with socioeconomic indicators at the ward level. The analysis for this paper was conducted using R @citeR, with several packages from the tidyverse suite (REFERENCE WICKHAM ETA) being used for data cleaning, manipulation and visualization. Visualizations were created using ggplot2, and tables were rendered using kableExtra.

>>>>

These datasets were merged in order to link capital funding allocations with socioeconomic indicators at the ward level. The analysis for this paper was conducted using @citeR, with several packages from the @tidyverse suite being used for data cleaning, manipulation and visualization. Visualizations were created using @ggplot2, and tables were rendered using kableExtra.
